---
title: "colourgen"
output: 
  github_document:
    toc: true
    fig_width: 8
    fig_height: 5
pkgdown:
  as_is: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Install

Install using `devtools::install_github("cjtexas/colourgen")`

The `colourgen` package provides a single, simple interface for generating colour palettes in R. `colourgen::make_palette` is the main function and returns a `colourgen` object with very handy `plot` and `print` methods to make generating, inspecting and fine-tuning color palettes a breeze.

The `colour` parameter will accept any base R color function, `RColorBrewer` named palette, `viridis` named palette, [color-hex](https://www.color-hex.com/color-palettes/) palette ID or variable-length character vector of any combination of base `grDevices::colours` and/or hexadecimal colors.

At the time I created this package there weren't enough good diverging palettes and I tend to use them alot in my work, so `colourgen` will default to some right out-of-the box.


`colourgen::make_palette()`
```{r, echo=FALSE}
plot(colourgen::make_palette())
```

```{r, echo=TRUE}
my_palette <- colourgen::make_palette(default = FALSE)
plot(my_palette)
```

If you like tweaking your color palettes, you can easily do that. Let's just simply replace the middle color with "ivory" and call `colourgen::make_palette` again to check the new results.

```{r, echo=TRUE}
my_palette[4] <- "ivory"
my_palette_mod <- colourgen::make_palette(colour = my_palette)
plot(my_palette_mod)
```


### No Limitations

If you want to interpolate a palette that normally has a hard limit; don't worry, `colourgen` was created for this very reason and wil return as many colors as you need for your factor levels! *NOTE:, you should still be careful and use common sense ;)*

`colourgen::make_palette(colour = "set1", n = 15)`

```{r, echo=FALSE}
plot(colourgen::make_palette(colour = "set1", 15))
```


### color-hex API

`colourgen` also supports the [color-hex](https://www.color-hex.com/color-palettes/) palette API. Just supply a valid paletteID and you can interpolate over that palette 'til your heart's content.

`colourgen::make_palette(colour = 1010612, n = 7)`

```{r, echo=FALSE}
plot(colourgen::make_palette(colour = 1010612, n = 7))
```


### Image Sampling

`colourgen` will also accept an image path or url. For example, let's make a palette from the R logo!

`colourgen::make_palette(colour = "http://r-project.org/Rlogo.png", n = 7)`

```{r, echo=FALSE}
plot(colourgen::make_palette(colour = "https://r-project.org/Rlogo.png", n = 7))
```

### Other Options

`colourgen` will let you shuffle or reverse the returned palette if you need to.

`colourgen::make_palette(colour = "set3", n = 9, shuffle = TRUE)`

```{r, echo=FALSE}
plot(colourgen::make_palette(colour = "set3", n = 9, shuffle = T))
```


`colourgen::make_palette(colour = "Purples", n = 15, reverse = TRUE)`

```{r, echo=FALSE}
plot(colourgen::make_palette(colour = "Purples", n = 15, reverse = T))
```


### Summary

`colourgen` aims to be a simple, but effective solution to the common task of crafting and previewing color palettes from many diverse sources. I hope you find it useful and also feel free to make pull/merge requests for bugs and improvements or adding new features if you like. 
